### 2012-07-30 inst/examples/managed_warning.Rmd
managed warning debug - rlnorm

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning/" or`

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 200
sigma_g <- .1
````

@@

``` {r noise}
z_g <- function() dlnorm(1, 0, sigma_g)
````

@@

``` {r  simulate }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

>>>>

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning2/" or`

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 200
sigma_g <- .2
x0 <- 2
````

@@

``` {r noise}
z_g <- function() rlnorm(1, 0, sigma_g)
````

@@

``` {r  simulate }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=x0, opt$D, z_g, z_m, z_i)
})
````
